Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: upd caption in corner plot in appendix

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
but without (blue contours)\agcomm{colors to be updated.} and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
%
\hs{We also need to fix overlapping tick labels.}
}
\label{fig:corner_plot_all}
\end{figure*}

>>>>

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $M_f$ for GW150914, using the same waveform model,
but without (purple contours) and with the non-GR parameters different from zero (blue contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
%
We observe the same qualitative behavior in the posteriors for the other modified gravity theories
studied in the main text.
}
\label{fig:corner_plot_all}
\end{figure*}
